A state space model for discovering the trajectory dynamics of replay

### 2020-03-05 Article.tex
Update on Overleaf.

\documentclass[times, twoside, watermark]{zHenriquesLab-StyleBioRxiv}
\usepackage{blindtext}
\pdfoptionalwaysusepdfpagebox=5
\DeclareMathOperator*{\E}{\mathbb{E}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}

@@

Current methods analyze hippocampal sequences by assuming a constant velocity trajectory (Davidson et al. 2009), corresponding to a single dynamic. This is done by computing the probability of position at each time using the place field information from the population of neurons and then fitting a line to maximize the probability of position over time. If the probabilities near the best fit line are high relative to shuffled distribution, the replay is analyzed. Often, trajectories that travel less than a certain distance (Pfeiffer and Foster 2013, Pfeiffer and Foster 2015) are excluded.

However, there is a growing evidence that trajectories that have more complex dynamics. Farooq and Dragoi (2019) found that juvenile rats . For example, Pfeiffer and Foster (2015) found that trajectories alternated between stationary hovering trajectories and continuous movement trajectories on a gamma timescale.

@@

Just for kicks here's a citation \cite{DavidsonHippocampalReplayExtended2009}. And a reference to a supplement \cref{note:Note1}. And \nameref{note:Note1}.
\Blindtext

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{figures/Figure1/Figure1_v3.pdf}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:computerNo}
\end{figure*}

\Blindtext

Figure \ref{fig:computerNo} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide. Use \verb|\begin{SCfigure*}...\end{SCfigure*}| for a wide figure with side captions.

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure2/Figure2_v3.pdf}
\caption{Model can classify each category of trajectory dynamic (and combinations of dynamics) on simulated data. Each panel has three plots that show (from top to bottom) the simulated cell population activity, the probability of the three trajectory dynamics at each time, and the decoded posterior probability of position at each time. \textbf{a.} Continuous. \textbf{b.} Hover. \textbf{c.} Fragmented. \textbf{d.} Hover-Continuous-Hover. \textbf{e.} Fragmented-Continuous-Fragmented. \textbf{f.} Fragmented-Hover-Fragmented.}
\label{fig:computerNo}
\end{figure*}

@@

blablaba \ref{fig:computerNo} 
\blindtext

\subsection*{Blabla} 
\blindtext

blablaba \ref{fig:computerNo}
\blindtext

\begin{acknowledgements}
\blindtext
\end{acknowledgements}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure1-supplemental1/Figure1_v1_supplemental1.pdf}
\caption{Increasing the probability of transitioning within category.}
\label{fig:Supplemental Figure 3}
\end{figure*}

>>>>

\documentclass[times, twoside]{zHenriquesLab-StyleBioRxiv}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\DeclareMathOperator*{\E}{\mathbb{E}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}

@@

Current methods analyze hippocampal sequences by assuming a constant velocity trajectory \cite{DavidsonHippocampalReplayExtended2009}, corresponding to a single dynamic. This is done by computing the probability of position at each time using the place field information from the population of neurons and then fitting a line to maximize the probability of position over time. If the probabilities near the best fit line are high relative to shuffled distribution, the replay is analyzed. Often, trajectories that travel less than a certain distance \cite{PfeifferAutoassociativedynamicsgeneration2015} are excluded.

However, there is a growing evidence that trajectories that have more complex dynamics. Farooq and Dragoi \cite{FarooqEmergencepreconfiguredplastic2019} found that juvenile rats . For example, Pfeiffer and Foster \cite{PfeifferAutoassociativedynamicsgeneration2015} found that trajectories alternated between stationary hovering trajectories and continuous movement trajectories on a gamma timescale.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1/Figure1_v3.pdf}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{Figure1}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2/Figure2_v3}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{Figure2}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure3/Figure3_v3}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{Figure3}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure4/Figure4_v2}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{Figure4}
\end{figure*}

@@

\subsection*{Blabla}

\begin{acknowledgements}
\end{acknowledgements}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1-supplemental1/Figure1_v1_supplemental1}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:Figure1-Figure supplement 1}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2-supplemental1/Figure2_v2-supplemental1}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:Figure2-Figure supplement 1}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2-supplemental2/Figure2_v2-supplemental2}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:Figure2-Figure supplement 2}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure3-supplemental1/Figure3_v2_supplemental1}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:Figure3-Figure supplement 1}
\end{figure*}
